How is experience transformed into memory?

### 2018-09-03 paper/main.tex
backup up progress (working on Methods, minor edits to results, added Quail reference).  all JRM NOTE issues have now been addressed, modulo existing github issues related to figure images

\newcommand{\topics}{S1}
\newcommand{\corrmats}{S2}
\newcommand{\matchmats}{S3}
\newcommand{\featureimportance}{S4}
\newcommand{\listlearning}{S5}

@@

The above results indicate that both the structure of the original video and participants' recalls of the video exhibit event boundaries that can be identified automatically by characterizing the dynamic content using a shared topic model and segmenting the content into events using HMMs.  Next we asked whether some correspondence might be made between the specific content of the events the participants experienced in the video, and the events they later recalled.  One approach to linking the experienced (video) and recalled events is to label each recalled event as matching the video event with the most similar (i.e., most highly correlated) topic vector (Figs.~\ref{fig:model}G, \matchmats).  This yields a sequence of ``presented'' events from the original movie, and a sequence of (potentially differently ordered) ``recalled'' events for each participant.  Analogous to classic list-learning studies, we can then examine participants' recall sequences by asking which events they tended to recall first~\citep[e.g., probability of first recall; Fig.~\listlearning A; ][]{WelcBurn24, PostPhil65, AtkiShif68}; how participants most often transition between recalls of the events as a function of the temporal distance between them~\citep[e.g., lag-conditional response probability; Fig.~\listlearning B; ][]{Kaha96}; and which events they were likely to remember overall~\citep[e.g., serial position recall analyses; Fig.~\listlearning C; ][]{Murd62a}.  In list-learning studies, this set of three analyses may be used to gain a nearly complete view into the sequences of recalls participants made~\citep[e.g., ][]{Kaha12}.  However, in naturalistic recall the analyses provide a wholly incomplete picture: they leave out any attempt to quantify participants' abilities to capture the \textit{content} of what occurred in the video (i.e., their only experimental instruction!).

@@

We created similar topic proportion matrices using hand-annotated transcripts of each participant's recall of the video~\citep[annotated by ][]{ChenEtal17}.  We tokenized the transcript into a list of sentences, and then re-organized the list into overlapping sliding windows spanning 10 sentences each; we in turn transformed each window's sentences into a word count vector (using the same vocabulary as for the video model).  We then used the topic model already trained on the video scenes to compute the most probable topic proportions for each sliding window.  This yielded a number-of-sentences (range: 68--294) by number-of-topics (100) topic proportions matrix, for each participant.  These reflected the dynamic content of each participant's recalls.

\paragraph*{Choosing topic model parameters}
\textbf{JRM NOTE: NEED TO DISCUSS THIS SECTION.  ALSO, I HAVE NOT EDITING THE WORDING.}
There were 3 critical parameters related to fitting the topic model: 1) the number of topics, 2) the window size of text descriptions of the video used to fit the model, and 3) the window size of recall sentences used to transform the recall data.  To chose these parameter values, we performed a grid search where the range of possible parameter values was 1, 5, 10, 25, 50, 100, 200, and 500. Our optimization objective was defined as the correlation between the hand annotated memory performance and the root mean squared distance between the video model and the recall model before any further processing (e.g., hidden Markov modeling, averaging within event, etc). While many of the parameter combination elicited moderately high correlations, the optimal choice was 100 topics, 50 video segments and 10 recall sentences.
%ACH NOTE: I did run this analysis, but before that i arbitrarily selected some parameters that ended up being very close to the best.  The reason I bring this up is that the correlations between some of the memory metrics (k, precision, distinctiveness) and hand annotated accuracy could be biased because we searched for the optimal parameters. Its not `the same' measure, but they are related to each other, so we'll have to be extra careful not to over interpret the correlations in this study.

>>>>

\newcommand{\topics}{S1}
\newcommand{\corrmats}{S2}
\newcommand{\matchmats}{S3}
\newcommand{\featureimportance}{S4}
\newcommand{\listlearning}{S5}
\newcommand{\topicopt}{S6}

@@

The above results indicate that both the structure of the original video and participants' recalls of the video exhibit event boundaries that can be identified automatically by characterizing the dynamic content using a shared topic model and segmenting the content into events using HMMs.  Next we asked whether some correspondence might be made between the specific content of the events the participants experienced in the video, and the events they later recalled.  One approach to linking the experienced (video) and recalled events is to label each recalled event as matching the video event with the most similar (i.e., most highly correlated) topic vector (Figs.~\ref{fig:model}G, \matchmats).  This yields a sequence of ``presented'' events from the original movie, and a sequence of (potentially differently ordered) ``recalled'' events for each participant.  Analogous to classic list-learning studies, we can then examine participants' recall sequences by asking which events they tended to recall first~\citep[e.g., probability of first recall; Fig.~\listlearning A; ][]{WelcBurn24, PostPhil65, AtkiShif68}; how participants most often transition between recalls of the events as a function of the temporal distance between them~\citep[e.g., lag-conditional response probability; Fig.~\listlearning B; ][]{Kaha96}; and which events they were likely to remember overall~\citep[e.g., serial position recall analyses; Fig.~\listlearning C; ][]{Murd62a}.  In list-learning studies, this set of three analyses may be used to gain a nearly complete view into the sequences of recalls participants made~\citep[e.g., ][]{Kaha12}.  Extending these analyses to apply to naturalistic stimuli and recall~\citep{HeusEtal17b} highlights that, in naturalistic recall, these analyses provide a wholly incomplete picture: they leave out any attempt to quantify participants' abilities to capture the \textit{content} of what occurred in the video (i.e., their only experimental instruction!).

@@

We created similar topic proportion matrices using hand-annotated transcripts of each participant's recall of the video~\citep[annotated by ][]{ChenEtal17}.  We tokenized the transcript into a list of sentences, and then re-organized the list into overlapping sliding windows spanning 10 sentences each; we in turn transformed each window's sentences into a word count vector (using the same vocabulary as for the video model).  We then used the topic model already trained on the video scenes to compute the most probable topic proportions for each sliding window.  This yielded a number-of-sentences (range: 68--294) by number-of-topics (100) topic proportions matrix, for each participant.  These reflected the dynamic content of each participant's recalls.  Note: for details on how we selected the video and recall window lengths and number of topics, see \textit{Supplemental Materials} and Figure~\topicopt.
